---
title: "Experimental Data of Cascade Experiments in Genomics"
author: "Frédéric Bertrand and Myriam Maumy-Bertrand"
output: github_document
---

[![CRAN status](https://www.r-pkg.org/badges/version/CascadeData)](https://cran.r-project.org/package=CascadeData)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi=150,fig.width=7
)
```
# CascadeData

The goal of CascadeData is to provide experimental data that are used as examples by packages such as the Cascade one, a modeling tool allowing gene selection, reverse engineering, and prediction in cascade networks. (Jung, N., Bertrand, F., Bahram, S., Vallat, L., and Maumy-Bertrand, M., 2014, <http://dx.doi.org/10.1093/bioinformatics/btt705>).

## Installation

You can install the released version of CascadeData from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("CascadeData")
```

## Examples

Two data frames with 54613 probesets measured 6 times throught 4 time points.

```{r exampleS}
data(micro_S)
str(micro_S)
```

```{r exampleUS}
data(micro_US)
str(micro_US)
```

You can also embed plots, for example:

```{r heatmapS, echo = FALSE}
heatmap(as.matrix(t(micro_S[1:200,])))
```

```{r heatmapUS, echo = FALSE}
heatmap(as.matrix(t(micro_US[1:200,])))
```

